\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{assignment 1}
\author{Dhananjay singh}
\date{2022A1R018}

\begin{document}

\maketitle

 \textbf{subject:} Invitation to be Keynote Speaker at International Conference on Latest Trends and Ethical Issues in AI-based Product Deployment in Markets

 respected Mr. Pichai,

 I hope this letter finds you in good health and high spirits. On behalf of the organizing committee of the MIET jammu, it is my honor to extend an invitation to you to be a keynote speaker at our prestigious event.

 The MIET organising committee is a globally recognized event that brings together professionals, researchers, and industry experts from various sectors to discuss the latest trends and ethical issues surrounding AI-based product deployment in markets.


      Conference details:


    Name: MIET AI organisation

    
    Date: 22 Aug, 2023

    
    Venue: MIET Jammu

    
    Theme: Latest Trends and Ethical Issues in AI-based Product Deployment in Markets.

    We kindly request your presence as a keynote speaker to deliver an address on the current trends, challenges, and ethical considerations in deploying AI-based products in markets. Your experience as the CEO of Google and your involvement in the development and deployment of innovative AI technologies make you an ideal candidate to address these critical topics.

    We eagerly await your response and sincerely hope that you will accept our invitation. Should you have any queries or require further information, please do not hesitate to contact me at 2022A1R018@mietjammu.in or 959-XXX-XXX.

    Thank you for considering our invitation, and we look forward to the possibility of your esteemed presence at the conference.

Yours sincerely,

Dhananjay singh jammoria


committee member


MIET Jammu AI/ML Organisation
\end{document}
